### 2012-10-10 docs/architecture/architecture.tex
new directory structure

\begin{figure}[]
\centering
\includegraphics[scale=0.55]{\archfigpath/maestro_ecosystem2}
\caption[\maestro\ `ecosystem'] {\label{fig:arch:eco} The basic
  \maestro\ `ecosystem'.  Here we see the different packages that
  contribute to building the {\tt test2} problem in \maestro.  The
  purple lines show the directories that are pulled in through
  variable Makefile variables ({\tt BOXLIB\_HOME}, {\tt NETWORK\_DIR},
  {\tt EOS\_DIR}, and {\tt CONDUCTIVITY\_DIR}).  The blue lines show
  standard modules that are used in most \maestro\ builds.}
\end{figure}

@@

  \item {\tt constants/}

    A simple module to define physical constants

@@

@@

  \item {\tt SCIENCE/}

@@

  \item {\tt Source\_SDC/}

    Source for an alternate formulation of \maestro\ that removes the
    splitting between hydrodynamics, diffusion, and reactions (see
    Chapter~\ref{ch:sdc}).

>>>>

\begin{figure}[]
\centering
\includegraphics[scale=0.55]{\archfigpath/maestro_ecosystem2}
\caption[\maestro\ `ecosystem'] {\label{fig:arch:eco} The basic
  \maestro\ `ecosystem'.  Here we see the different packages that
  contribute to building the {\tt test2} problem in \maestro.  The
  red directories are part of most standard \maestro\ build.  The
  purple lines show the directories that are pulled in through
  various Makefile variables ({\tt BOXLIB\_HOME}, {\tt NETWORK\_DIR},
  {\tt EOS\_DIR}, and {\tt CONDUCTIVITY\_DIR}).}
\end{figure}

@@

@@

  \item {\tt Exec/}

    The various problem-setups.

    \begin{itemize}
    \item {\tt SCIENCE/}

@@

@@
